Make maps of loan words

### 2025-03-26 analysis/paper/paper.qmd
change data cleaning code

```{r clean duplicates}
# Function to remove duplicates
remove_duplicates <- function(df_list) {
  df_list <- lapply(df_list, function(df) {
    df <- df |> 
      dplyr::distinct(glott_code, form, .keep_all = TRUE)
    return(df)
  })
  return(df_list)
}

@@

```{r}
#| label: fonio
#| fig-cap: "fonio word forms"
 create_leaflet_map(data_list[[1]], background = "bw")
```

@@

```{r}
#| label: save-maps
#| eval: false
save_maps(data_list)
```

>>>>

```{r clean duplicates}
# Function to remove duplicates
remove_duplicates <- function(df_list) {
  df_list <- lapply(df_list, function(df) {
    df <- df |> 
      dplyr::distinct(glott_code, style, .keep_all = TRUE)
    return(df)
  })
  return(df_list)
}

@@

```{r}
#| label: fonio
#| fig-cap: "fonio word forms"
# create_leaflet_map(data_list$iron, background = "bw")
```

@@

```{r}
#| label: save-maps
#| eval: false
# save_maps(data_list)
```
